\input{../utils/slide-preamble1.tex}
\input{../utils/slide-preamble2.tex}
\input{../utils/macros.tex}
% \bibliography{../bib/references}
\bibliography{references}
\input{../utils/title-info.tex}

\usetheme{default}
\usecolortheme{default}

% remove footer
\setbeamertemplate{footline}{}

\newif\ifsectiona
% \sectionatrue

\newif\ifquant
% \quanttrue

\ifsectiona%
    \newcommand{\sectionaonly}[1]{#1}%
\else%
    \newcommand{\sectionaonly}[1]{}%
\fi

\ifquant%
    \newcommand{\quantonly}[1]{#1}%
\else%
    \newcommand{\quantonly}[1]{}%
\fi

\title[Exam Information]{Exam Information}
\date{\today}

\begin{document}
\begin{frame}
    \begin{itemize}
        \item Please clear your desks so we can pass out exams.
% 1. Be sure that your cell phones are completely off
        \item Cell phones completely off and put away.
% 2. Please reserve left-handed desks for left-handed people
        \item Please reserve left-handed desks for left-handed people.
% 3. Please reserve the front row and seats on the aisle for people who are
% learning English and may need to ask clarification questions.
        \item Please reserve the front row and aisle seats for
            non-native English speakers.
% 4. Packs and other gear under your chairs, please, so we can get into your
% row to answer questions.
        \quantonly{\item Get your calculator out now. We have some in front, but you
            cannot take them to your seat.}
        \item Packs and other gear under your chairs, please.
        \item We will post corrections or clarifications on the front screen.
        \item We will update the time remaining every 5 minutes.
        \item Baseball caps on backwards and hoodies down, please---we need to
            see your smiling faces!
        \item When I call time, you must stop \textbf{IMMEDIATELY}. You may not
            write \textbf{AT ALL} after time is called.
% 8. (Section A only) Remember to exit from the back when you're done with the
% exam, so the next class can come in.
        \sectionaonly{ \item Please exit from the back, so the next class can
            come in.  }
% 9. As soon as the room is quiet and desktops are empty, we're ready to pass
% out the exams ... please take one, leave it face down, and pass the stack
% along, face down. Put an exam face down on any empty desk. If you do this
% quickly, we can start before the bell rings.
        \item When we pass out exams, please take one, leave it face down, and
            pass the stack along, face down. Put an exam face down on any empty
            desk.
% You can call the start as soon as everyone has an exam.
    \end{itemize}
\end{frame}

\begin{frame}[t]
    \begin{center}
        \vspace{0.5cm}
        {\Huge Time remaining: 2}
    \end{center}

        % \vspace{0.5cm}
        % \begin{enumerate}
        %     \item
        % \end{enumerate}
\end{frame}


\end{document}

